---
title: "p 180233 - Weighting Walkthrough"
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 5
    toc_float: yes
    number_sections: yes
  html_notebook:
    df_print: paged
    number_sections: yes
    toc: yes
    toc_depth: 5
    toc_float: yes
date: "`r format(Sys.time(), '%d/%m/%Y')`"
---

```{r 'options', echo=FALSE, message=FALSE}
source('../scripts/checkpoint.R')
```

```{r 'data load', echo=FALSE, message=FALSE}
source('../scripts/01_load.R')
```

# Descriptive Analysis

We begin with a high-level description of our data to ensure all the relevant measures are being used and matched observed tabs obtained from DP.

## Q9 Patient Case Load
```{r 'q9_descr', echo=FALSE}
d2 <- d1[, c(id_mask, 'country', q9_mask), with = F] %>% 
  data.table::melt.data.table(id.vars = c(id_mask, 'country'),
                              variable.factor = FALSE)

d$labels[d2, on = 'variable'] %>% 
  .[, mean(value), by = c('country', 'label', 'variable')] %>% 
  data.table::dcast.data.table(variable + label ~ country, value.var = 'V1') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average Patient Load - Q9') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

d$labels[d2, on = 'variable'] %>% 
  .[, sum(!is.na(value)), by = c('country', 'label', 'variable')] %>% 
  data.table::dcast.data.table(variable + label ~ country, value.var = 'V1') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Bases - Q9') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

```

## Q11 Patient Progresion to Prostate Cancer
```{r 'q11_descr', echo=FALSE}
d2 <- d1[, c(id_mask, 'country', q11_mask), with = F] %>% 
  data.table::melt.data.table(id.vars = c(id_mask, 'country'),
                              variable.factor = FALSE)

d$labels[d2, on = 'variable'] %>% 
  .[, mean(value, na.rm = TRUE), by = c('country', 'label', 'variable')] %>% 
  data.table::dcast.data.table(variable + label ~ country, value.var = 'V1') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average Proportional Progression (%) - Q11') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

d$labels[d2, on = 'variable'] %>% 
  .[, sum(!is.na(value)), by = c('country', 'label', 'variable')] %>% 
  data.table::dcast.data.table(variable + label ~ country, value.var = 'V1') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Bases - Q11') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))
```

## Q12 Length of Time to Progression
```{r 'q12_descr', echo=FALSE}
d2 <- d1[, c(id_mask, 'country', 'q12new_tot_1', 'q12new_tot_2'), with = F] %>% 
  data.table::melt.data.table(id.vars = c(id_mask, 'country'),
                              variable.factor = FALSE)

d$labels[d2, on = 'variable'] %>% 
  .[, mean(value), by = c('country', 'label', 'variable')] %>% 
  data.table::dcast.data.table(variable + label ~ country, value.var = 'V1') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average Time to Progression (months) - Q12') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

d$labels[d2, on = 'variable'] %>% 
  .[, sum(!is.na(value)), by = c('country', 'label', 'variable')] %>% 
  data.table::dcast.data.table(variable + label ~ country, value.var = 'V1') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Bases - Q12') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

```

## Q25 Metasttic Castrate REsistant Prostate Case Load
```{r 'q25_descr', echo=FALSE}
d2 <- d1[, c(id_mask, 'country', q25_mask), with = F] %>% 
  data.table::melt.data.table(id.vars = c(id_mask, 'country'),
                              variable.factor = FALSE)

d$labels[d2, on = 'variable'] %>% 
  .[, mean(value, na.rm = TRUE), by = c('country', 'label', 'variable')] %>% 
  data.table::dcast.data.table(variable + label ~ country, value.var = 'V1') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average Patient Load - Q25') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

d$labels[d2, on = 'variable'] %>% 
  .[, sum(!is.na(value)), by = c('country', 'label', 'variable')] %>% 
  data.table::dcast.data.table(variable + label ~ country, value.var = 'V1') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Bases - Q25') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

```

## Q26 Metastatic Castrate Resistant Prostate Cancer (M1 CR PC) currently on 1st line treatment Case Load
```{r 'q26_descr', echo=FALSE}
d2 <- d1[, c(id_mask, 'country', q26b_mask), with = F] %>% 
  data.table::melt.data.table(id.vars = c(id_mask, 'country'),
                              variable.factor = FALSE)

d$labels[d2, on = 'variable'] %>% 
  .[, mean(value, na.rm = TRUE), by = c('country', 'label', 'variable')] %>% 
  data.table::dcast.data.table(variable + label ~ country, value.var = 'V1') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average Treatment Duration (months) - Q26') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

d$labels[d2, on = 'variable'] %>% 
  .[, sum(!is.na(value)), by = c('country', 'label', 'variable')] %>% 
  data.table::dcast.data.table(variable + label ~ country, value.var = 'V1') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Bases - Q26') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

```


## Q27 Metastatic Castrate Resistant Prostate Cancer (M1 CR PC) currently on 2nd line treatment 
```{r 'q27_descr', echo=FALSE}
d2 <- d1[, c(id_mask, 'country', q27b_mask), with = F] %>% 
  data.table::melt.data.table(id.vars = c(id_mask, 'country'),
                              variable.factor = FALSE)

d$labels[d2, on = 'variable'] %>% 
  .[, mean(value, na.rm = TRUE), by = c('country', 'label', 'variable')] %>% 
  data.table::dcast.data.table(variable + label ~ country, value.var = 'V1') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average Treatment Duration (months) - Q27') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

d$labels[d2, on = 'variable'] %>% 
  .[, sum(!is.na(value)), by = c('country', 'label', 'variable')] %>% 
  data.table::dcast.data.table(variable + label ~ country, value.var = 'V1') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Bases - Q27') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

```

# Weight Calculations

## LOC/LAPC
```{r loc_weights, echo=FALSE}
d1[, 'q9_prop_q11_1' := q9_a_1 * q11_1/100]
d1[, 'q9_prop_q11_2' := q9_a_1 * q11_2/100]

d1[, c(id_mask, 'country', 'q9_a_1', q11_mask, 'q9_prop_q11_1', 'q9_prop_q11_2'), with = F] %>% 
  head(10) %>% print

d1[, c('country', 'q9_prop_q11_1'), with = F] %>% 
  .[, mean(q9_prop_q11_1, na.rm = TRUE), by = 'country'] %>% 
  data.table::setnames('V1', 'Re-prop. Q9') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average case load, reproportioned by progression to M0 HS PC - Q9_1 * Q11_1') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

d1[, c('country', 'q9_prop_q11_2'), with = F] %>% 
  .[, mean(q9_prop_q11_2, na.rm = TRUE), by = 'country'] %>% 
  data.table::setnames('V1', 'Re-prop. Q9') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average case load, reproportioned by progression to M1 HS PC - Q9_1 * Q11_2') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))


aux_d <- d1[, c('country', 'q9_prop_q11_1', 'q9_prop_q11_2'), with = F] %>% 
  .[, list(mean(q9_prop_q11_1, na.rm = TRUE),
           mean(q9_prop_q11_2, na.rm = TRUE)),
    by = 'country'] %>% 
  data.table::setnames(c('V1', 'V2'), c('q9_prop_q11_1_mean','q9_prop_q11_2_mean'))

d1 <- d1[aux_d, on = 'country']

d1[, 'weight_1_1' := q9_prop_q11_1/q9_prop_q11_1_mean] %>% 
  .[, 'weight_1_1' := ifelse(weight_1_1 > 3, 3, weight_1_1)] %>% 
  .[, 'weight_1_1' := ifelse(weight_1_1 < 0.3, 0.3, weight_1_1)]

d1[, 'weight_1_2' := q9_prop_q11_2/q9_prop_q11_2_mean] %>% 
  .[, 'weight_1_2' := ifelse(weight_1_2 > 3, 3, weight_1_2)] %>% 
  .[, 'weight_1_2' := ifelse(weight_1_2 < 0.3, 0.3, weight_1_2)]

d1[, c(id_mask, 
       'country', 
       'q9_a_1', 
       q11_mask, 
       'q9_prop_q11_1', 
       'q9_prop_q11_2', 
       'q9_prop_q11_1_mean', 
       'q9_prop_q11_2_mean', 
       'weight_1_1', 'weight_1_2'), with = F] %>% 
  head(10) %>% 
  print

d1[['weight_1_1']] %>% hist(main = 'weight_1_1')
d1[['weight_1_2']] %>% hist(main = 'weight_1_2')
```

## M0 HS
```{r m0hs_weights, echo=FALSE}
d1[, 'q9_prop_q14_1' := q9_a_3 * q14_1/100]
d1[, 'q9_prop_q14_2' := q9_a_3 * q14_2/100]
d1[, 'q9_prop_q14_3' := q9_a_3 * q14_3/100]

d1[, c(id_mask, 'country', 'q9_a_3', q14_mask, 'q9_prop_q14_1', 'q9_prop_q14_2', 'q9_prop_q14_3'), with = F] %>% 
  head(10) %>% print

d1[, c('country', 'q9_prop_q14_1'), with = F] %>% 
  .[, mean(q9_prop_q14_1, na.rm = TRUE), by = 'country'] %>% 
  data.table::setnames('V1', 'Re-prop. Q9') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average case load, reproportioned by progression to M0 CR PC - Q9_3 * Q14_1') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

d1[, c('country', 'q9_prop_q14_2'), with = F] %>% 
  .[, mean(q9_prop_q14_2, na.rm = TRUE), by = 'country'] %>% 
  data.table::setnames('V1', 'Re-prop. Q9') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average case load, reproportioned by progression to M1 HS PC - Q9_3 * Q14_2') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

d1[, c('country', 'q9_prop_q14_3'), with = F] %>% 
  .[, mean(q9_prop_q14_3, na.rm = TRUE), by = 'country'] %>% 
  data.table::setnames('V1', 'Re-prop. Q9') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average case load, reproportioned by progression to M1 CR PC - Q9_3 * Q14_3') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))


aux_d <- d1[, c('country', 'q9_prop_q14_1', 'q9_prop_q14_2', 'q9_prop_q14_3'), with = F] %>% 
  .[, list(mean(q9_prop_q14_1, na.rm = TRUE),
           mean(q9_prop_q14_2, na.rm = TRUE),
           mean(q9_prop_q14_3, na.rm = TRUE)),
    by = 'country'] %>% 
  data.table::setnames(c('V1', 'V2', 'V3'), c('q9_prop_q14_1_mean','q9_prop_q14_2_mean', 'q9_prop_q14_3_mean'))

d1 <- d1[aux_d, on = 'country']

d1[, 'weight_2_1' := q9_prop_q14_1/q9_prop_q14_1_mean] %>% 
  .[, 'weight_2_1' := ifelse(weight_2_1 > 3, 3, weight_2_1)] %>% 
  .[, 'weight_2_1' := ifelse(weight_2_1 < 0.3, 0.3, weight_2_1)]

d1[, 'weight_2_2' := q9_prop_q14_2/q9_prop_q14_2_mean] %>% 
  .[, 'weight_2_2' := ifelse(weight_2_2 > 3, 3, weight_2_2)] %>% 
  .[, 'weight_2_2' := ifelse(weight_2_2 < 0.3, 0.3, weight_2_2)]

d1[, 'weight_2_3' := q9_prop_q14_3/q9_prop_q14_3_mean] %>% 
  .[, 'weight_2_3' := ifelse(weight_2_3 > 3, 3, weight_2_3)] %>% 
  .[, 'weight_2_3' := ifelse(weight_2_3 < 0.3, 0.3, weight_2_3)]

d1[, c(id_mask, 
       'country', 
       'q9_a_3', 
       q14_mask, 
       'q9_prop_q14_1', 
       'q9_prop_q14_2',
       'q9_prop_q14_3',
       'q9_prop_q14_1_mean', 
       'q9_prop_q14_2_mean',
       'q9_prop_q14_3_mean',
       'weight_2_1', 'weight_2_2', 'weight_2_3'), with = F] %>% 
  head(10) %>% 
  print

d1[['weight_2_1']] %>% hist(main = 'weight_2_1')
d1[['weight_2_2']] %>% hist(main = 'weight_2_2')
d1[['weight_2_3']] %>% hist(main = 'weight_2_3')
```

## mCRPC L1
```{r mcrpsl1_weights, echo=FALSE}
d1[, 'q9_prop_q25_1' := q9_a_7 * q25_1/100]

d1[, c(id_mask, 'country', 'q9_a_7', 'q25_1', 'q9_prop_q25_1'), with = F] %>% 
  head(10) %>% print

d1[, c('country', 'q9_prop_q25_1'), with = F] %>% 
  .[, mean(q9_prop_q25_1, na.rm = TRUE), by = 'country'] %>% 
  data.table::setnames('V1', 'Re-prop. Q9') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average case load, reproportioned by progression to mCRPC L1 - Q9_7 * Q25_1') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

aux_d <- d1[, c('country', 'q9_prop_q25_1'), with = F] %>% 
  .[, list(mean(q9_prop_q25_1, na.rm = TRUE)),
    by = 'country'] %>% 
  data.table::setnames(c('V1'), c('q9_prop_q25_1_mean'))

d1 <- d1[aux_d, on = 'country']

d1[, 'weight_3_1' := q9_prop_q25_1/q9_prop_q25_1_mean] %>% 
  .[, 'weight_3_1' := ifelse(weight_3_1 > 3, 3, weight_3_1)] %>% 
  .[, 'weight_3_1' := ifelse(weight_3_1 < 0.3, 0.3, weight_3_1)]

d1[, c(id_mask, 
       'country', 
       'q9_a_7', 
       'q25_1', 
       'q9_prop_q25_1', 
       'q9_prop_q25_1_mean',
       'weight_3_1'), with = F] %>% 
  head(10) %>% 
  print

d1[['weight_3_1']] %>% hist(main = 'weight_3_1')
```


## mCRPC L2
```{r mcrpsl2_weights, echo=FALSE}
d1[, 'q9_prop_q25_2' := q9_a_7 * q25_2/100]

d1[, c(id_mask, 'country', 'q9_a_7', 'q25_2', 'q9_prop_q25_2'), with = F] %>% 
  head(10) %>% print

d1[, c('country', 'q9_prop_q25_2'), with = F] %>% 
  .[, mean(q9_prop_q25_2, na.rm = TRUE), by = 'country'] %>% 
  data.table::setnames('V1', 'Re-prop. Q9') %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Average case load, reproportioned by progression to mCRPC L2 - Q9_7 * Q25_2') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))

aux_d <- d1[, c('country', 'q9_prop_q25_2'), with = F] %>% 
  .[, list(mean(q9_prop_q25_2, na.rm = TRUE)),
    by = 'country'] %>% 
  data.table::setnames(c('V1'), c('q9_prop_q25_2_mean'))

d1 <- d1[aux_d, on = 'country']

d1[, 'weight_3_2' := q9_prop_q25_2/q9_prop_q25_2_mean] %>% 
  .[, 'weight_3_2' := ifelse(weight_3_2 > 3, 3, weight_3_2)] %>% 
  .[, 'weight_3_2' := ifelse(weight_3_2 < 0.3, 0.3, weight_3_2)]

d1[, c(id_mask, 
       'country', 
       'q9_a_7', 
       'q25_2', 
       'q9_prop_q25_2', 
       'q9_prop_q25_2_mean',
       'weight_3_2'), with = F] %>% 
  head(10) %>% 
  print

d1[['weight_3_2']] %>% hist(main = 'weight_3_2')
```

# Weighted Means and Medians

## LOC/LAPC
```{r loc_out_stats, echo=FALSE}
out_1 <- data.table::rbindlist(list(d1[, .(country, 
                                           q12new_tot_1,
                                           q12new_tot_2,
                                           weight_1_1,
                                           weight_1_2)] %>% 
                                      .[complete.cases(.)] %>% 
                                      .[, list(M0HsPC_wtmean = weighted.mean(q12new_tot_1, weight_1_1),
                                               M0HsPC_wtmedian = matrixStats::weightedMedian(q12new_tot_1, weight_1_1),
                                               M1HsPC_wtmean = weighted.mean(q12new_tot_2, weight_1_2),
                                               M1HsPC_wtmedian = matrixStats::weightedMedian(q12new_tot_2, weight_1_2))] %>% 
                                      .[, 'country' := 'Total'],
                                    d1[, .(country, 
                                           q12new_tot_1,
                                           q12new_tot_2,
                                           weight_1_1,
                                           weight_1_2)] %>% 
                                      .[complete.cases(.)] %>% 
                                      .[, list(M0HsPC_wtmean = weighted.mean(q12new_tot_1, weight_1_1),
                                               M0HsPC_wtmedian = matrixStats::weightedMedian(q12new_tot_1, weight_1_1),
                                               M1HsPC_wtmean = weighted.mean(q12new_tot_2, weight_1_2),
                                               M1HsPC_wtmedian = matrixStats::weightedMedian(q12new_tot_2, weight_1_2)),
                                        by = 'country']),
                               use.names = TRUE) %>% 
  data.table::setcolorder(c(5, 1:4)) %>% 
  data.table::melt.data.table(id.vars = 'country',
                              variable.name = 'variable') %>% 
  .[, 'stat' := stringr::str_replace(variable, '.*_','')] %>% 
  .[, 'stage' := stringr::str_replace(variable, '_.*', '')] %>% 
  .[, 'variable' := NULL] %>% 
  data.table::dcast.data.table(country + stat ~ stage, 
                               value.var = 'value') %>% 
  .[, 'LOC/LAPC' := (M0HsPC + M1HsPC)/2] %>% 
  .[order(stat)]

out_1 %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Weighted time to progression (months) LOC/LAPC') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))
```

## M0 HS
```{r m0hs_out_stats, echo=FALSE}
out_2 <- data.table::rbindlist(list(d1[, .(country, 
                                           q15new_tot_1,
                                           q15new_tot_2,
                                           q15new_tot_3,
                                           weight_2_1,
                                           weight_2_2,
                                           weight_2_3)] %>% 
                                      .[complete.cases(.)] %>% 
                                      .[, list(M0CRPC_wtmean = weighted.mean(q15new_tot_1, weight_2_1),
                                               M0CRPC_wtmedian = matrixStats::weightedMedian(q15new_tot_1, weight_2_1),
                                               M1HsPC_wtmean = weighted.mean(q15new_tot_2, weight_2_2),
                                               M1HsPC_wtmedian = matrixStats::weightedMedian(q15new_tot_2, weight_2_2),
                                               M1CRPC_wtmean = weighted.mean(q15new_tot_3, weight_2_3),
                                               M1CRPC_wtmedian = matrixStats::weightedMedian(q15new_tot_3, weight_2_3))] %>% 
                                      .[, 'country' := 'Total'],
                                    d1[, .(country, 
                                           q15new_tot_1,
                                           q15new_tot_2,
                                           q15new_tot_3,
                                           weight_2_1,
                                           weight_2_2,
                                           weight_2_3)] %>% 
                                      .[complete.cases(.)] %>% 
                                      .[, list(M0CRPC_wtmean = weighted.mean(q15new_tot_1, weight_2_1),
                                               M0CRPC_wtmedian = matrixStats::weightedMedian(q15new_tot_1, weight_2_1),
                                               M1HsPC_wtmean = weighted.mean(q15new_tot_2, weight_2_2),
                                               M1HsPC_wtmedian = matrixStats::weightedMedian(q15new_tot_2, weight_2_2),
                                               M1CRPC_wtmean = weighted.mean(q15new_tot_3, weight_2_3),
                                               M1CRPC_wtmedian = matrixStats::weightedMedian(q15new_tot_3, weight_2_3)),
                                        by = 'country']),
                               use.names = TRUE) %>% 
  data.table::setcolorder(c(5, 1:4)) %>% 
  data.table::melt.data.table(id.vars = 'country',
                              variable.name = 'variable') %>% 
  .[, 'stat' := stringr::str_replace(variable, '.*_','')] %>% 
  .[, 'stage' := stringr::str_replace(variable, '_.*', '')] %>% 
  .[, 'variable' := NULL] %>% 
  data.table::dcast.data.table(country + stat ~ stage, 
                               value.var = 'value') %>% 
  .[, 'M0HS' := (M0CRPC + M1CRPC + M1HsPC)/3] %>% 
  .[order(stat)]

out_2 %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Weighted time to progression (months) M0 HS') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))
```


## mCPRC L1
```{r mcprcl1_out_stats, echo=FALSE}
out_3 <- data.table::rbindlist(list(d1[, .(country, 
                                           q26duration,
                                           weight_3_1)] %>% 
                                      .[complete.cases(.)] %>% 
                                      .[, list(mCRPCL1_wtmean = weighted.mean(q26duration, weight_3_1),
                                               mCRPCL1_wtmedian = matrixStats::weightedMedian(q26duration, weight_3_1))] %>% 
                                      .[, 'country' := 'Total'],
                                    d1[, .(country, 
                                           q26duration,
                                           weight_3_1)] %>% 
                                      .[complete.cases(.)] %>% 
                                      .[, list(mCRPCL1_wtmean = weighted.mean(q26duration, weight_3_1),
                                               mCRPCL1_wtmedian = matrixStats::weightedMedian(q26duration, weight_3_1)),
                                        by = 'country']),
                               use.names = TRUE) %>% 
  data.table::setcolorder(c(3, 1:1))

out_3 %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Weighted time to progression (months) mCRPC L1') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))
```


## mCPRC L2
```{r mcprcl2_out_stats, echo=FALSE}
out_3 <- data.table::rbindlist(list(d1[, .(country, 
                                           q27duration,
                                           weight_3_2)] %>% 
                                      .[complete.cases(.)] %>% 
                                      .[, list(mCRPCL2_wtmean = weighted.mean(q27duration, weight_3_2),
                                               mCRPCL2_wtmedian = matrixStats::weightedMedian(q27duration, weight_3_2))] %>% 
                                      .[, 'country' := 'Total'],
                                    d1[, .(country, 
                                           q27duration,
                                           weight_3_2)] %>% 
                                      .[complete.cases(.)] %>% 
                                      .[, list(mCRPCL2_wtmean = weighted.mean(q27duration, weight_3_2),
                                               mCRPCL2_wtmedian = matrixStats::weightedMedian(q27duration, weight_3_2)),
                                        by = 'country']),
                               use.names = TRUE) %>% 
  data.table::setcolorder(c(3, 1:1))

out_3 %>% 
  kableExtra::kable(digits = 1,
                    escape = F,
                    caption = 'Weighted time to progression (months) mCRPC L2') %>% 
  kableExtra::kable_styling(full_width = FALSE, 
                            position = 'center',
                            bootstrap_options = c("striped", "hover"))
```

